Corpus Analysis

### 2020-05-15 evaluation/R/corpus-analysis.Rmd
Updates in corpus analysis

```{r summary}
summary_corpus <- function(df, prefix) {
  overview_table(
    r(paste(prefix, "cran"), df),
    r(paste(prefix, "installed"), filter(df, installed)),
    r(paste(prefix, "loadable"), filter(df, loadable)),

@@

    r(paste(prefix, "with coverage"), filter(df, coverage_expr > 0)),
    r(paste(prefix, "mean expr coverage"), percent(mean(df$coverage_expr, na.rm=T))),
    r(paste(prefix, "median expr coverage"), percent(median(df$coverage_expr, na.rm=T))),

@@

    r(paste(prefix, "mean revdes"), mean(df$revdeps, na.rm=T)),
    r(paste(prefix, "median revdes"), median(df$revdeps, na.rm=T)),

    r(paste(prefix, "runtime"), as.duration(sum(df$runnable_time, na.rm=T))),
    r(paste(prefix, "mean runtime"), as.duration(mean(df$runnable_time, na.rm=T))),
    r(paste(prefix, "median runtime"), as.duration(median(df$runnable_time, na.rm=T))),

    r(paste(prefix, "using roxygen"), sum(df$uses_roxygen, na.rm=T))
  )
}

>>>>

```{r summary}
summary_corpus <- function(df, prefix) {
  w_coverage <- filter(df, coverage_expr > 0)
  w_revdeps <- filter(df, revdeps > 0)
  w_runnable <- filter(df, !is.na(runnable_time))

  overview_table(
    r(paste(prefix, "cran"), df),
    r(paste(prefix, "installed"), filter(df, installed)),
    r(paste(prefix, "loadable"), filter(df, loadable)),

@@

    r(paste(prefix, "with coverage"), w_coverage),
    r(paste(prefix, "mean expr coverage"), percent(mean(w_coverage))),
    r(paste(prefix, "median expr coverage"), percent(median(w_coverage))),

@@

    r(paste(prefix, "w revdes"), w_revdeps),
    r(paste(prefix, "mean revdes"), mean(w_revdeps)),
    r(paste(prefix, "median revdes"), median(w_revdeps)),
    r(paste(prefix, "at least min revdep"), filter(w_revdeps, revdeps >= params$min_revdeps)),

    r(paste(prefix, "runtime"), as.duration(sum(w_runnable$runnable_time))),
    r(paste(prefix, "mean runtime"), as.duration(mean(w_runnable$runnable_time))),
    r(paste(prefix, "median runtime"), as.duration(median(w_runnable$runnable_time))),

    r(paste(prefix, "using roxygen"), sum(df$uses_roxygen, na.rm=T)),
  )
}
